---
title: "Correlation"
author: "Oleksandr Koval"
format: 
  html: 
    toc: true
    toc-location: right
    self-contained: true
    code-line-numbers: true
editor: visual
---

# Create data

```{r}
#| Label: Creating data
#| code-summary: Creating data
#| results: false
#| code-fold: true
#| warning: false

library(tidyverse)
library(ggplot2)

b <- c(1, 2, 3, 4, 5, 6, 7, 8, 9, 10) %>% tibble()
c <- c(18, 36, 60, 12, 6, 30, 72, 24, 42, 60) %>% tibble()

ds0 <- 
  bind_cols(b, c) %>%  
  setNames(c("x", "y"))  

ds0 %>% 
  tibble() %>% 
  glimpse()

b_1 <- c(1, 2, 3, 4, 5, 6, 7, 8, 9, 10) %>% tibble()
c_1 <- c(2, 4, 6, 8, 10, 12, 14, 16, 18, 20) %>% tibble()

ds1 <- 
  bind_cols(b_1, c_1) %>%  
  setNames(c("x", "y"))  


ds1 %>% 
  tibble() %>% 
  glimpse()

ds2 <- 
  ds1 %>% 
  mutate(x = rev(x))

ds2 %>% glimpse()

b_2 <- c( 1, 2, 3, 4, 5, 6, 7, 8, 9, 10) %>% tibble()
c_2 <- c(1, 4, 9, 16, 25, 36, 49, 64, 81, 100) %>% tibble()

ds3 <- 
  bind_cols(b_2, c_2) %>%  
  setNames(c("x", "y"))  

ds3 %>% glimpse()

ds4 <- 
  ds3 %>% 
  mutate(x = rev(x))

ds_function <- function(x) {
  y <- 2*x
  return(y)
}
ds5 <- tibble(x = seq(0, 10, 1), y = ds_function(seq(0, 10, 1)))
ds5 %>% glimpse()
```

# Positive/Negative line

```{r}
#| Label: Exploring 
#| code-summary: Exploring 
#| results: markup
#| code-fold: true

ds0 %>% 
  ggplot(aes(x = x, y = y)) +
  geom_point() +
  theme_minimal() +
  scale_x_continuous(breaks = seq(0, 10, 1)) +
  scale_y_continuous(breaks = seq(0,72, 6)) # Creating the graph between x and y arguments 

```

We can see that the graph has not any correlation between x and y.

## Positive line correlation

```{r}
#| Label: Exploring 2
#| code-summary: Exploring 2
#| results: markup
#| code-fold: true


ds1 %>% 
  ggplot(aes(x=x,y=y))+
  geom_point() +
  theme_minimal() +
  scale_x_continuous(breaks = seq(0, 10, 1)) +
  scale_y_continuous(breaks = seq(0,20, 2)) +
  geom_line() 
```

We can see that the graph has **line positive correlation** between x and y.

## Negative line correlation

```{r}
#| Label: Exploring 3
#| code-summary: Exploring 3
#| results: markup
#| code-fold: true

ds2 %>% 
  ggplot(aes(x=x,y=y))+
  geom_point() +
  theme_minimal() +
  scale_x_continuous(breaks = seq(0, 10, 1)) +
  scale_y_continuous(breaks = seq(0,20, 2)) +
  geom_line() 

```

We can see that the graph has **line negative correlation** between x and y.

# Positive/Negative not line correlation

## Positive square correlation

```{r}
#| Label: Exploring 4
#| code-summary: Exploring 4
#| results: markup
#| code-fold: true

ds3 %>% 
  ggplot(aes(x = x, y = y)) +
  geom_point() +
  geom_line() +
  theme_minimal() + 
  scale_x_continuous(breaks = seq(0,10,1)) + 
  scale_y_continuous(breaks = seq(0,100,10))

```

We can see that the graph has **positive square correlation** between x and y.

## Negative square correlation

```{r}
#| Label: Exploring 5
#| code-summary: Exploring 5
#| results: markup
#| code-fold: true

ds4 %>% 
  ggplot(aes(x = x, y = y)) +
  geom_point() +
  geom_line() +
  theme_minimal() + 
  scale_x_continuous(breaks = seq(0,10,1)) + 
  scale_y_continuous(breaks = seq(0,100,10))

```

We can see that the graph has **negative square correlation** between x and y.

# Differnce between correlation and relation

If we change one of arguments in correlation another argument **wont change**

If we change one argument in relation another argument **will change**

In relation arguments interconnected, in correlation not

## Correlation with changed data

```{r}
#| Label: Example 1
#| code-summary: Ecample
#| results: hold
#| code-fold: true

ds1 %>% 
  mutate(
    x = c(5, 2, 3, 4, 5, 6, 7, 8, 9, 10)
  ) %>%  
  ggplot(aes(x=x,y=y))+
  geom_point() +
  theme_minimal() +
  scale_x_continuous(breaks = seq(0, 10, 1)) +
  scale_y_continuous(breaks = seq(0,20, 2)) +
  geom_line() 

```

## Relation with changed data

```{r}
#| Label: Example 2
#| code-summary: Ecample
#| results: hold
#| code-fold: true

ds5 %>% 
  mutate(
    x = seq(0, 10, 1,) + pi
  ) %>% 
  ggplot(aes(x=x,y=y))+
  geom_point() +
  theme_minimal() +
  scale_x_continuous(breaks = seq(0, 10, 1)) +
  scale_y_continuous(breaks = seq(0,20, 2)) +
  geom_line() 
```

We can see that in correlation y not changed when we change x. Despite, in relation if we changed x, y also will change.
