---
title: "Comparing Ukrainian Universities"
author: "Oleksandr Koval"
format: 
  revealjs:
    theme: night
    transition: slide
---

## Introduction

---

<div style="text-align: left; font-size:1.3em;">
<strong>Two Friends, Two Stories</strong><br><br>
Sasha lives in Vinnytsia, Bill — in Dnipro. Both have just finished school and face a classic dilemma:<br>
<span class="fragment highlight-current-blue" style="color:#FFC300;font-weight:bold">
Where to go next, to not only get a degree, but to truly open doors for the future?
</span>
</div>

---

<div style="text-align: left; font-size:1.15em;">
<strong>Dreams and Doubts</strong><br>
Sasha dreams of big cities — he is drawn to Kyiv or Lviv, vast campuses, prestigious universities, new startups and interesting people.<br>
But he wonders: if he stays in Vinnytsia, close to family and friends, is that really a step back?<br>
<span class="fragment fade-in" style="color:#FFC300;font-weight:bold">
VNTU is a strong local technical university — maybe it’s not a compromise after all.
</span>
</div>

---

<div style="text-align: left; font-size:1.15em;">
<strong>Bill’s Perspective</strong><br>
Bill wants to be an IT specialist or engineer. He loves his home city, but hears so many cool things about “top universities”.<br>
<span class="fragment fade-in" style="color:#FFC300;font-weight:bold">
Would a KPI or Lviv Polytech diploma really open more doors?
</span><br>
Or will staying at NTUDP in Dnipro — with local connections and lower costs — be the smarter move?
</div>

---

<div style="text-align: left; font-size:1.15em;">
<strong>The Eternal Dilemma</strong><br>
They keep returning to the same questions:
<ul style="color:#FFC300; font-weight:bold; margin-left: 1.2em;">
  <li class="fragment">Is a “top” university really worth it?</li>
  <li class="fragment">Does comfort and familiar surroundings matter more at the start of adult life?</li>
  <li class="fragment">Where is it easier to find friends, inspiration, and a first job?</li>
  <li class="fragment">How to see beyond “prestige” and find real opportunities?</li>
</ul>
</div>

---

<div style="text-align: left; font-size:1.15em;">
<strong>This Presentation = Their Decision Map</strong><br>
Sasha and Bill decide to be rational:<br>
<span class="fragment fade-in" style="color:#FFC300;font-weight:bold">
They compare universities by rankings, accessibility, student life, and future perspectives.
</span><br>
This presentation is not just numbers — it’s a <span class="fragment highlight-current-blue" style="color:#FFC300;font-weight:bold">real decision map</span> for every graduate at this crossroads.
</div>

---

## Data Overview

- Data: a table of universities (student numbers, city, rankings, applications)
- Source: 1-scribe-ds3.rds

``` {r}
library(tidyverse)
ds3 <- readRDS("C:/Users/muaro/Documents/GitHub/applied-math-stories/data-private/derived/university-ranking/1-scribe-ds3.rds")
theme_set(
  theme_minimal(base_size = 18) +
    theme(
      panel.background = element_rect(fill = "#171a21", color = NA),
      plot.background  = element_rect(fill = "#171a21", color = NA),
      plot.title       = element_text(face = "bold", hjust = 0.5, size = 22, color = "#FFF"),
      axis.title       = element_text(size = 16, color = "#AEEFFF"),
      axis.text        = element_text(size = 14, color = "#E1E8ED"),
      panel.grid.major = element_line(color = "#223", size = 0.5),
      panel.grid.minor = element_blank()
    )
)
summary(ds3)
```

---

## 1. Experience & Location

---

### Why does location matter?

- Your university city is not just about education — it's your lifestyle for 4–6 years.
- The city will shape your friends, routine, impressions, and even career options.
- Look not just at rankings, but also at comfort, adaptation, and city opportunities.

---

### Advantages of Top Universities (Kyiv, Lviv, Big Cities)

- More specialties, modern labs, stronger academic programs.
- Lots of clubs, events, international exchanges.
- Active city life: concerts, startups, communities, networking.
- Prestigious diplomas are valued by employers.
- Opportunities for internships in big or international companies.

---

### Disadvantages of Top Universities and Big Cities

- Higher competition for entry and during studies, harder to stand out.
- Expensive accommodation, food, and entertainment.
- Far from home and family — adaptation can be tough.
- Risk of “getting lost in the crowd” in a big city without strong support.

---

### Advantages of a Local University (Vinnytsia, Dnipro)

- Easier adaptation: familiar city, family and friends close by.
- Lower costs for living.
- Smaller groups, closer contact with professors.
- Easier to get first internships and jobs in the local area.
- Less stress from city bustle, more time for hobbies or self-development.

---

### Disadvantages of a Local University


- Fewer specialties, less access to advanced labs and international projects.
- Fewer student organizations and large-scale events.
- Need to work harder for national or international opportunities.
- Smaller cities sometimes offer fewer options for growth outside your main specialty.

---

## 2. International Attitude

- Comparison by international rankings:
    - Scopus Rank
    - Webometrics Rank
    - QS Rank
    - Times Higher Education (THE)
    - QS Sustainability

---

## VNTU — Vinnytsia National Technical University

- VNTU is the leading technical university in Vinnytsia and the region.
- Focus: engineering, IT, energy, construction.
- Strong ties to local business, modern facilities, active student life.
- Chosen by graduates from Vinnytsia, Khmelnytskyi, Zhytomyr regions who want a strong degree in their home area.

---

## "Top Universities" vs VNTU: Scopus Rank

``` {r}
d1 <- ds3 %>% filter(school_abb %in% c("KPI", "KNUTS", "LKPI", "VNTU"))
ggplot(d1, aes(x = school_abb, y = scopus_rank)) +
  geom_point(data = filter(d1, school_abb == "VNTU"), fill = "#FFEB3B", size = 6, shape = 21, alpha = 0.95, color = "#222") +
  geom_point(data = filter(d1, school_abb != "VNTU"), size = 6, fill = "#00B8D9", color = "#BDBDBD", shape = 21, alpha = 0.9) +
  scale_y_reverse() +
  geom_text(aes(label = school_abb), fontface = "bold", size = 5, nudge_y = -2.5, color = "#FFF") +
  labs(x = "University", y = "Scopus Rank", title = "Scopus Ranking (VNTU vs Top)")
```

---

## "Top Universities" vs VNTU: Webometrics Rank

``` {r}
ggplot(d1, aes(x = school_abb, y = webometrics_rank)) +
  geom_point(data = filter(d1, school_abb == "VNTU"), fill = "#FFEB3B", size = 6, shape = 21, alpha = 0.95, color = "#222") +
  geom_point(data = filter(d1, school_abb != "VNTU"), size = 6, fill = "#00B8D9", color = "#BDBDBD", shape = 21, alpha = 0.9) +
  scale_y_reverse() +
  geom_text(aes(label = school_abb), fontface = "bold", size = 5, nudge_y = -2.5, color = "#FFF") +
  labs(x = "University", y = "Webometrics Rank", title = "Webometrics Ranking")
```

---

## "Top Universities" vs VNTU: QS Rank

``` {r}
ggplot(d1, aes(x = school_abb, y = qs_rank)) +
  geom_point(data = filter(d1, school_abb == "VNTU"), fill = "#FFEB3B", size = 6, shape = 21, alpha = 0.95, color = "#222") +
  geom_point(data = filter(d1, school_abb != "VNTU"), size = 6, fill = "#00B8D9", color = "#BDBDBD", shape = 21, alpha = 0.9) +
  scale_y_reverse() +
  geom_text(aes(label = school_abb), fontface = "bold", size = 5, nudge_y = -0.5, color = "#FFF") +
  labs(x = "University", y = "QS Rank", title = "QS Ranking")
```

---

## "Top Universities" vs VNTU: THE World University Ranking

``` {r}
ggplot(d1, aes(x = school_abb, y = wur_rank)) +
  geom_point(data = filter(d1, school_abb == "VNTU"), fill = "#FFEB3B", size = 6, shape = 21, alpha = 0.95, color = "#222") +
  geom_point(data = filter(d1, school_abb != "VNTU"), size = 6, fill = "#00B8D9", color = "#BDBDBD", shape = 21, alpha = 0.9) +
  scale_y_reverse() +
  geom_text(aes(label = school_abb), fontface = "bold", size = 5, nudge_y = -0.5, color = "#FFF") +
  labs(x = "University", y = "THE Rank", title = "Times Higher Education Ranking")
```

---

## "Top Universities" vs VNTU: QS Sustainability Ranking

``` {r}
ggplot(d1, aes(x = school_abb, y = qswur_rank)) +
  geom_point(data = filter(d1, school_abb == "VNTU"), fill = "#FFEB3B", size = 6, shape = 21, alpha = 0.95, color = "#222") +
  geom_point(data = filter(d1, school_abb != "VNTU"), size = 6, fill = "#00B8D9", color = "#BDBDBD", shape = 21, alpha = 0.9) +
  scale_y_reverse() +
  geom_text(aes(label = school_abb), fontface = "bold", size = 5, nudge_y = -0.5, color = "#FFF") +
  labs(x = "University", y = "QS Sustainability", title = "QS Sustainability Ranking")
```

---

## NTUDP — Dnipro National Technical University of Railway Transport

- NTUDP is the main technical university of Dnipro.
- Specializes in transport, engineering, IT, and applied sciences.
- Regionally significant, convenient for students from eastern and central Ukraine.
- Often chosen by local school graduates wanting to stay in Dnipro or pursue technical specialties.

---

## "Top Universities" vs NTUDP: Scopus Rank

``` {r}
d2 <- ds3 %>% filter(school_abb %in% c("KPI", "KNUTS", "LKPI", "NTUDP"))
ggplot(d2, aes(x = school_abb, y = scopus_rank)) +
  geom_point(data = filter(d2, school_abb == "NTUDP"), fill = "#FF5252", size = 6, shape = 21, alpha = 0.95, color = "#FFF") +
  geom_point(data = filter(d2, school_abb != "NTUDP"), size = 6, fill = "#00B8D9", color = "#BDBDBD", shape = 21, alpha = 0.9) +
  scale_y_reverse() +
  geom_text(aes(label = school_abb), fontface = "bold", size = 5, nudge_y = -2.5, color = "#FFF") +
  labs(x = "University", y = "Scopus Rank", title = "Scopus Ranking (NTUDP vs Top)")
```

---

## "Top Universities" vs NTUDP: Webometrics Rank

``` {r}
ggplot(d2, aes(x = school_abb, y = webometrics_rank)) +
  geom_point(data = filter(d2, school_abb == "NTUDP"), fill = "#FF5252", size = 6, shape = 21, alpha = 0.95, color = "#FFF") +
  geom_point(data = filter(d2, school_abb != "NTUDP"), size = 6, fill = "#00B8D9", color = "#BDBDBD", shape = 21, alpha = 0.9) +
  scale_y_reverse() +
  geom_text(aes(label = school_abb), fontface = "bold", size = 5, nudge_y = -2.5, color = "#FFF") +
  labs(x = "University", y = "Webometrics Rank", title = "Webometrics Ranking")
```

---

## "Top Universities" vs NTUDP: QS Rank

``` {r}
ggplot(d2, aes(x = school_abb, y = qs_rank)) +
  geom_point(data = filter(d2, school_abb == "NTUDP"), fill = "#FF5252", size = 6, shape = 21, alpha = 0.95, color = "#FFF") +
  geom_point(data = filter(d2, school_abb != "NTUDP"), size = 6, fill = "#00B8D9", color = "#BDBDBD", shape = 21, alpha = 0.9) +
  scale_y_reverse() +
  geom_text(aes(label = school_abb), fontface = "bold", size = 5, nudge_y = -0.5, color = "#FFF") +
  labs(x = "University", y = "QS Rank", title = "QS Ranking")
```

---

## "Top Universities" vs NTUDP: THE World University Ranking

``` {r}
ggplot(d2, aes(x = school_abb, y = wur_rank)) +
  geom_point(data = filter(d2, school_abb == "NTUDP"), fill = "#FF5252", size = 6, shape = 21, alpha = 0.95, color = "#FFF") +
  geom_point(data = filter(d2, school_abb != "NTUDP"), size = 6, fill = "#00B8D9", color = "#BDBDBD", shape = 21, alpha = 0.9) +
  scale_y_reverse() +
  geom_text(aes(label = school_abb), fontface = "bold", size = 5, nudge_y = -0.5, color = "#FFF") +
  labs(x = "University", y = "THE Rank", title = "Times Higher Education Ranking")
```

---

## "Top Universities" vs NTUDP: QS Sustainability Ranking

``` {r}
ggplot(d2, aes(x = school_abb, y = qswur_rank)) +
  geom_point(data = filter(d2, school_abb == "NTUDP"), fill = "#FF5252", size = 6, shape = 21, alpha = 0.95, color = "#FFF") +
  geom_point(data = filter(d2, school_abb != "NTUDP"), size = 6, fill = "#00B8D9", color = "#BDBDBD", shape = 21, alpha = 0.9) +
  scale_y_reverse() +
  geom_text(aes(label = school_abb), fontface = "bold", size = 5, nudge_y = -0.5, color = "#FFF") +
  labs(x = "University", y = "QS Sustainability", title = "QS Sustainability Ranking")
```

---

## 3. Total University's Rank in 2024

---

### What is "Total University's Rank"?

- The EuroOsvita 2024 total rank is the most authoritative national university ranking.
- It combines multiple metrics: international reputation, research, student success, and innovation.
- Used by applicants, employers, and policymakers to assess university quality.

---

### Why Does It Matter?

- <span class="fragment highlight-current-blue" style="color:#FFC300;font-weight:bold">For graduates</span>: Helps to understand not only "big names", but real performance.<br>
- <span class="fragment highlight-current-blue" style="color:#FFC300;font-weight:bold">For families</span>: Indicates where your investment in education will give the best result.<br>
- <span class="fragment highlight-current-blue" style="color:#FFC300;font-weight:bold">For universities</span>: Shows areas for growth and competition.

---

### How Do Local and Top Universities Compare?

- Top universities (KPI, KNUTS, LKPI) usually dominate the upper ranks.
- Local leaders (like VNTU, NTUDP) can outperform some "big" universities in focused specialties or regional impact.
- The "total" rank shows the real position of your future diploma on the Ukrainian market.


---

### Where Do "Top" and "Local" Universities Stand?

``` {r}
selected_unis <- c("VNTU", "KPI", "LKPI", "KNUTS", "NTUDP")
ds3 %>% 
  filter(school_abb %in% selected_unis) %>%
  ggplot(aes(x = reorder(school_abb, rank_2024), y = rank_2024)) +
  geom_point(shape = 21, color = "white", size = 8, fill = "#00B8D9", alpha = 0.7) +
  geom_point(data = ds3 %>% filter(school_abb == "VNTU"), fill = "red", shape = 21, size = 8, color = "white", alpha = 0.9) +
  geom_point(data = ds3 %>% filter(school_abb == "NTUDP"), fill = "green", shape = 21, size = 8, color = "white", alpha = 0.9) +
  geom_text(aes(label = school_abb), fontface = "bold", size = 6, nudge_y = -2.5, color = "#FFF") +
  scale_y_reverse() +
  labs(
    title = "Rank 2024 for Selected Universities",
    x = "Abbreviation",
    y = "Place (Lower = Better)"
  )
```

---

### Key Takeaways

- "Top" universities secure leading places, but local leaders are not far behind.
- Choosing a university is about balancing ambition, comfort, and real prospects — not just chasing the top spot in the rankings!
- Always consider your own goals and values when reading the rankings.

---

## 4. Chances to Get In

---

### Total Applications

``` {r}
d4 <- ds3 %>% filter(school_abb %in% c("KPI", "KNUTS", "LKPI", "NTUDP", "VNTU"))
ggplot(d4, aes(x = school_abb, y = application_total_count)) +
  geom_col(fill = "#26C6DA", alpha = 0.82, color = "#121212") +
  geom_text(aes(label = application_total_count), 
            vjust = 1.5, size = 6, color = "#FFFDE7", fontface = "bold") +
  labs(x = "University", y = "Total Applications", title = "Total Applications")
```

---

### Budget Applications

``` {r}
ggplot(d4, aes(x = school_abb, y = application_budget_count)) +
  geom_col(fill = "#66BB6A", alpha = 0.84, color = "#121212") +
  geom_text(aes(label = application_budget_count), 
            vjust = 1.5, size = 6, color = "#FFFDE7", fontface = "bold") +
  labs(x = "University", y = "Budget Applications", title = "Budget Applications")
```

---

### Average Admission Score

``` {r}
ggplot(d4, aes(x = school_abb, y = score_mean)) +
  geom_col(fill = "#FFA726", alpha = 0.82, color = "#121212") +
  geom_text(aes(label = round(score_mean, 2)), 
            vjust = 1.5, size = 6, color = "#FFFDE7", fontface = "bold") +
  labs(x = "University", y = "Average Score", title = "Average Admission Score")
```

---

## 5. University's Activity

- Importance of scientific, social, and business activity.
- Additional opportunities for students.

---


## 6. Local Universities in Their Areas

---

### Why Compare Locally?

- National rankings show the “big picture,” but for most students, local reputation and options matter most.
- Let’s look at how VNTU and NTUDP stand out among all universities in their own regions.

---

### VNTU in Vinnytsia Region

- Vinnytsia region has several higher education institutions, but only one major technical university: VNTU.
- VNTU consistently ranks as the **#1 university in Vinnytsia oblast** in most years.
- Its regional leadership gives students an advantage in local industry, jobs, and innovation projects.

---

### Where Does VNTU Stand Locally?

``` {r}
# Filter Vinnytsia oblast universities and sort by rank_2024
vinnytsia_unis <- ds3 %>% filter(oblast == "Vinnytsia", !is.na(rank_2024)) %>%
  arrange(rank_2024)
ggplot(vinnytsia_unis, aes(x = reorder(school_abb, rank_2024), y = rank_2024, fill = (school_abb == "VNTU"))) +
  geom_col(width = 0.65, color = "#121212", alpha = 0.88, show.legend = FALSE) +
  scale_fill_manual(values = c(`TRUE` = "#FFC300", `FALSE` = "#0099CC")) +
  geom_text(aes(label = rank_2024), vjust = -.65, size = 6, color = "#FFFDE7", fontface = "bold") +
  scale_y_reverse() +
  labs(
    title = "Universities in Vinnytsia Oblast by Total Rank (2024)",
    x = "University (abbr.)",
    y = "Rank (lower is better)"
  ) +
  theme_minimal(base_size = 18) +
  theme(
    panel.background = element_rect(fill = "#171a21", color = NA),
    plot.background = element_rect(fill = "#171a21", color = NA),
    plot.title = element_text(face = "bold", hjust = 0.5, size = 22, color = "#FFF"),
    axis.title = element_text(size = 16, color = "#AEEFFF"),
    axis.text = element_text(size = 14, color = "#E1E8ED"),
    panel.grid.major = element_line(color = "#223", size = 0.5),
    panel.grid.minor = element_blank()
  )
```

---

### Local Insights: Vinnytsia

- <span class="fragment highlight-current-blue" style="color:#FFC300;font-weight:bold">VNTU</span> is not just a local leader—it’s the clear top choice for technical and engineering careers in the oblast.
- The gap between VNTU and other Vinnytsia universities is significant, especially in technology fields.
- Employers in the region often prioritize VNTU graduates.

---

### NTUDP in Dnipropetrovsk Region

- Dnipropetrovsk oblast has many universities, including national and medical institutions.
- NTUDP is the **#1 technical university in the region**—often top-3 overall in the oblast.
- The city of Dnipro is a major educational center in eastern Ukraine.

---

### Where Does NTUDP Stand Locally?

``` {r}
# Filter Dnipropetrovsk oblast universities and sort by rank_2024
dnipro_unis <- ds3 %>% filter(oblast == "Dnipropetrovsk", !is.na(rank_2024)) %>%
  arrange(rank_2024)
ggplot(dnipro_unis, aes(x = reorder(school_abb, rank_2024), y = rank_2024, fill = (school_abb == "NTUDP"))) +
  geom_col(width = 0.65, color = "#121212", alpha = 0.88, show.legend = FALSE) +
  scale_fill_manual(values = c(`TRUE` = "#44e350", `FALSE` = "#0099CC")) +
  geom_text(
    aes(label = rank_2024),
    vjust = -0.5,
    size = 4,
    color = "#FFFDE7",
    fontface = "bold"
  ) +
  scale_y_reverse(expand = expansion(mult = c(0.05, 0.15))) +
  labs(
    title = "Universities in Dnipropetrovsk Oblast by Total Rank (2024)",
    x = "University (abbr.)",
    y = "Rank (lower is better)"
  ) +
  theme_minimal(base_size = 18) +
  theme(
    panel.background = element_rect(fill = "#171a21", color = NA),
    plot.background = element_rect(fill = "#171a21", color = NA),
    plot.title = element_text(face = "bold", hjust = 0.5, size = 22, color = "#FFF"),
    axis.title = element_text(size = 16, color = "#AEEFFF"),
    axis.text = element_text(size = 14, color = "#E1E8ED"),
    axis.text.x = element_text(size = 9, color = "#E1E8ED"),  # Abbreviation smaller here!
    panel.grid.major = element_line(color = "#223", size = 0.5),
    panel.grid.minor = element_blank(),
    plot.margin = margin(20, 30, 20, 30)
  )

```

---

### Local Insights: Dnipro

- <span class="fragment highlight-current-blue" style="color:#44e350;font-weight:bold">NTUDP</span> is a strong regional player and recognized technical leader in Dnipropetrovsk oblast.
- Dnipro offers many choices, but NTUDP’s niche in transport, engineering, and applied sciences sets it apart.
- For technical careers in the region, NTUDP’s diploma is highly valued by employers.

---

### Conclusions for Local Choices

- Both <span style="color:#FFC300;font-weight:bold">VNTU</span> (Vinnytsia) and <span style="color:#44e350;font-weight:bold">NTUDP</span> (Dnipro) are the clear top choices for technical education in their home oblasts.
- When considering where to study, check both the **national** and **local** rankings to maximize your future opportunities!

---

## Summary & Recommendations

- Choose your university wisely: base your decision on your own goals and the data.
- Top universities = more opportunities and prestige.
- Local universities = easier entry, comfort, community.


