---
title: "Example: Combined in Quarto"
author: "Andriy Koval, Oleksandr Koval"
format:
  html:
    page-layout: full
    toc: true
    toc-location: right
    code-fold: show
    theme: simplex
    highlight-style: github
    colde-line-numbers: true
    css: styles.css
    self-contained: true
editor: visual
editor_options: 
  chunk_output_type: console
---
This report examines rankings of Ukrainian universities in 2024 as reported by ... .

# Data

We extract the [data table](https://euroosvita.net/index.php/?category=49&id=8251) with university rankings for 2024 as reported by \[Euro Osvita\]\[https://euroosvita.net\].

```{r}
#| label: load-data-1
#| warning: false
library(tidyverse)
library(rvest)
library(ggplot2)

# Specify the URL of the webpage
url <- "https://euroosvita.net/index.php/?category=49&id=8251"

# Read the HTML content of the webpage
webpage <- read_html(url)

# Extract the table(s) from the HTML content
tables <- html_table(webpage, fill = TRUE)

# Access the desired table (may not be the first one)
ds0 <- tables[[5]] # the focal table of analysis, EUROOSVITA ranks
```

A [separate page](https://euroosvita.net/index.php/?category=1&id=8252) describes 10 indices used to compile the ranking.

```{r}
#| label: import-from-google-sheet
#| code-summary: Importing data from supporting google sheets
#| results: hide
#| cache: true
# we manually copy-paste Table 3 into a google spreadsheet, manually tweak,
# augment with additional variables, and inport into R.  Consider this workflow,
# as an alternative for using propriary software such as MS Excel
library(googlesheets4)
googlesheets4::gs4_deauth() # to indicate there is no need for a access token
# By default we will work with public Sheets
# but see https://googlesheets4.tidyverse.org/ for how to set access to private
# URL https://docs.google.com/spreadsheets/d/1Ha5JmJRzV1e2ljN3lNLu-pZJwyehJPoKrw9CtMvBMks/edit?usp=sharing
sheet_name <- "1es_-MBukFcmptQ6IvYmT1Q6kC2ZXHOye0IBPSQbChcQ"
tab_name1 <- "raw"
tab_name2 <- "input"

ds_edu_index <- read_sheet(sheet_name,tab_name2,skip = 0)
spreadsheet_url <- "https://docs.google.com/spreadsheets/d/1es_-MBukFcmptQ6IvYmT1Q6kC2ZXHOye0IBPSQbChcQ/edit?usp=sharing"
ds_edu_index %>% glimpse()


ds_school_meta <- 
  read_sheet(
    ss = "1MbTBWkIPMeIIjmLH4Q__TVWUg9y9KqTY34MwWYP0HoM"
    ,sheet = "Sheet1"
    ,skip = 0
) 
ds_school_meta %>% glimpse()

ds_school_meta2 <- 
  read_sheet(
    ss = "1MDc4A-_ueo7a90lxJBzIGE-VsKzwjkOTs7Oi_z1ZRsE"
    ,sheet = "Sheet2"
    ,skip = 0
  ) 

ds_school_meta2 %>% glimpse()

ds_myrank <- 
  read_sheet(
    ss = "1_JEO1ygEHbl6Gr5QX4Uj_v2M7J78ZAa283zXRqVD_Ns"
    ,sheet = "Sheet1"
    ,skip = 0
  ) %>% mutate(rank_2024 = rank(index_2024, ties.method = "min")) %>% select(rank_2024, everything())

ds_myrank %>% glimpse()
```

# Tweak Data 1

```{r}
#| label: tweak-data-1
#| code-summary: Wrangle data
#| results: hide

ds1_school_contex <- 
  ds_school_meta %>% 
  left_join(
    ds_school_meta2 %>% select(-school_name)
    ,by = "school_id"
  ) %>% 
  rename(
    student_count             = student_body_2024
    ,department_count         = num_faculty
    ,program_count            = num_specility     
    ,application_total_count  = num_requests
    ,application_budget_count = num_budget
    ,score_mean               = mean_bal
  ) 
ds1_school_contex %>% glimpse()

var_names <- c(
 "rank_2024"        = "РЕЙТИНГ  2024"
,"school_name"      = "ЗВО"
,"index_2024"       = "∑  ІНДЕКСІВ  ЗВО"
,"qs_rank"          = "Рейтинг  QS"
,"qs_index"         = "ІНДЕКС  для  QS"
,"scopus_rank"      = "Рейтинг  Scopus"
,"scopus_index"     = "ІНДЕКС  для  Scopus"
,"webometrics_rank" = "Рейтинг  Webometrics"
,"webometrics_index"= "ІНДЕКС  для  Webometrics"
,"uimpact_rank"     = "Рейтинг  THE  University  Impact"
,"uimpact_index"    = "ІНДЕКС  для  THE  University  Impact"
,"wur_rank"         = "Рейтинг  THE  WUR"
,"wur_index"        = "ІНДЕКС  для  THE  WUR"
,"qswur_rank"       = "QS  WUR  Sustainability"
,"qswur_index"      = "ІНДЕКС  для  QS  WUR  Sustainability"
,"competition_rank" = "Рейтинг  переможців  наукових  конкурсів"
,"competition_index"= "ІНДЕКС  для  переможців  наукових  конкурсів"
,"naqa_rank"        = "Рейтинг  Акредитаційних  справ  НАЗЯВО  2019-2023"
,"naqa_index"       = "ІНДЕКС  для  Акредитаційних  справ  НАЗЯВО  2019-2023"
,"patent_rank"      = "Рейтинг  за  кількістю  отриманих  патентів"
,"patent_index"     = "ІНДЕКС  для  отриманих  патентів"
,"mean_rank"        = "Середнє  арифметичне  рейтингових  місць  за  Заявами  вступників  та  СКБ"
,"mean_index"       = "ІНДЕКС  для  Заяв  вступників  та  СКБ"
)

ds0 %>% glimpse()
ds_names <- 
  ds0 %>% slice(1) %>% t() %>% 
  as_tibble() %>%
  rename(
    ua_name = V1
  ) 

ds1 <- 
  ds0 %>% 
  slice(2:nrow(ds0))   # Because it contains the names of the columns
  
names(ds1) <- names(var_names)
ds_names  %>% print(n=nrow(.))
ds0 %>% glimpse()
ds1 %>% glimpse()
```

# Tweek data 2

We can see that the *"index_2024"* directly proportional to *"rank_2024"*

We can see that the *"qs_index"* directly proportional to *"qs_rank"*

Also, the lowest value of *"qs_rank"* is 7

```{r}
#| label: tweek-data-2
#| code-summary: Preparing data to use 
#| warning: false
#| results: hold
#| code-fold: true

# At this point we have
ds1 %>% glimpse() # EUROOSVITA source
ds1_school_contex %>% glimpse()

convert_to_numeric <- function(x) {
  # Replace comma with dot
  x <- gsub(",", ".", x)
  # Convert to numeric
  as.numeric(x)
}

varnames_in_ds1 <- names(ds1)
varnames_to_convert_to_numeric <- setdiff(varnames_in_ds1, "school_name")


ds2 <- 
  ds1 %>% 
  mutate_at(
    .vars = varnames_to_convert_to_numeric
    ,.funs = ~convert_to_numeric(.)
  ) %>% 
  mutate(
    school_id = as.integer(rank_2024) # bc that's how we defined ID
  ) %>% 
  relocate(school_id) %>% 
  relocate(school_name,.after = "school_id")
  
# ds2 %>% glimpse()
ds1_school_contex %>% glimpse()

ds3 <- 
  ds2 %>%
  left_join(
    ds1_school_contex %>% select(-school_name, -rank_2024)
    ,by = "school_id"
  )

ds3 %>% glimpse()
```

# Explore

```{r}
#| code-summary: graph 1
#| 

# what university has the highest demand for budget places? 
ds3 %>% glimpse()
d1 <- 
  ds3 %>% 
  mutate(
    budget_ratio = application_budget_count/ application_total_count
  )
d1

g1 <- 
  d1 %>% 
  ggplot(aes(x=score_mean, y = budget_ratio, color = oblast))+
  # scale_x_continuous(limits = c(0,51))
  geom_point()+
  labs(
    title  = "Relationship between average submitted score and share of application for public funding"
    ,x = "Mean score of the application"
    ,y = "Share of application for public fundtion"
  )
g1
```
























