---
title: "Example: Combined in Quarto"
author: "Andriy Koval, Oleksandr Koval"
format:
  html:
    page-layout: full
    toc: true
    toc-location: right
    code-fold: show
    theme: simplex
    highlight-style: github
    colde-line-numbers: true
    css: styles.css
    self-contained: true
editor: visual
editor_options: 
  chunk_output_type: console
---
This report examines rankings of Ukrainian universities in 2024 as reported by ... .

# Data

We extract the [data table](https://euroosvita.net/index.php/?category=49&id=8251) with university rankings for 2024 as reported by \[Euro Osvita\]\[https://euroosvita.net\].

```{r}
#| label: load-data-1
#| warning: false
library(tidyverse)
library(rvest)
library(ggplot2)

# Specify the URL of the webpage
url <- "https://euroosvita.net/index.php/?category=49&id=8251"

# Read the HTML content of the webpage
webpage <- read_html(url)

# Extract the table(s) from the HTML content
tables <- html_table(webpage, fill = TRUE)

# Access the desired table (may not be the first one)
ds0 <- tables[[5]]
```

A [separate page](https://euroosvita.net/index.php/?category=1&id=8252) describes 10 indices used to compile the ranking.

```{r}
#| label: import-from-google-sheet
#| code-summary: Importing data from supporting google sheets

# we manually copy-paste Table 3 into a google spreadsheet, manually tweak,
# augment with additional variables, and inport into R.  Consider this workflow,
# as an alternative for using propriary software such as MS Excel
library(googlesheets4)
googlesheets4::gs4_deauth() # to indicate there is no need for a access token
# By default we will work with public Sheets
# but see https://googlesheets4.tidyverse.org/ for how to set access to private
# URL https://docs.google.com/spreadsheets/d/1Ha5JmJRzV1e2ljN3lNLu-pZJwyehJPoKrw9CtMvBMks/edit?usp=sharing
sheet_name <- "1es_-MBukFcmptQ6IvYmT1Q6kC2ZXHOye0IBPSQbChcQ"
tab_name1 <- "raw"
tab_name2 <- "input"

ds_edu_index <- read_sheet(sheet_name,tab_name2,skip = 0)
spreadsheet_url <- "https://docs.google.com/spreadsheets/d/1es_-MBukFcmptQ6IvYmT1Q6kC2ZXHOye0IBPSQbChcQ/edit?usp=sharing"
ds_edu_index %>% glimpse()


ds_school_meta <- 
  read_sheet(
    ss = "1MbTBWkIPMeIIjmLH4Q__TVWUg9y9KqTY34MwWYP0HoM"
    ,sheet = "Sheet1"
    ,skip = 0
) 
ds_school_meta %>% glimpse()

ds_school_meta2 <- 
  read_sheet(
    ss = "1MDc4A-_ueo7a90lxJBzIGE-VsKzwjkOTs7Oi_z1ZRsE"
    ,sheet = "Sheet2"
    ,skip = 0
  ) 

ds_school_meta2 %>% glimpse()
```

```{r}
#| label: tweak-data-1
#| code-summary: Wrangle data
var_names <- c(
 "rank_2024" = "РЕЙТИНГ  2024"
,"school_name" = "ЗВО"
,"index_2024" = "∑  ІНДЕКСІВ  ЗВО"
,"qs_rank" = "Рейтинг  QS"
,"qs_index" = "ІНДЕКС  для  QS"
,"scopus_rank" = "Рейтинг  Scopus"
,"scopus_index" = "ІНДЕКС  для  Scopus"
,"webometrics_rank" = "Рейтинг  Webometrics"
,"webometrics_index" = "ІНДЕКС  для  Webometrics"
,"uimpact_rank" = "Рейтинг  THE  University  Impact"
,"uimpact_index" = "ІНДЕКС  для  THE  University  Impact"
,"wur_rank" = "Рейтинг  THE  WUR"
,"wur_index" = "ІНДЕКС  для  THE  WUR"
,"qswur_rank" = "QS  WUR  Sustainability"
,"qswur_index" = "ІНДЕКС  для  QS  WUR  Sustainability"
,"competition_rank" = "Рейтинг  переможців  наукових  конкурсів"
,"competition_index" = "ІНДЕКС  для  переможців  наукових  конкурсів"
,"naqa_rank" = "Рейтинг  Акредитаційних  справ  НАЗЯВО  2019-2023"
,"naqa_index" = "ІНДЕКС  для  Акредитаційних  справ  НАЗЯВО  2019-2023"
,"patent_rank" = "Рейтинг  за  кількістю  отриманих  патентів"
,"patent_index" = "ІНДЕКС  для  отриманих  патентів"
,"mean_rank" = "Середнє  арифметичне  рейтингових  місць  за  Заявами  вступників  та  СКБ"
,"mean_index" = "ІНДЕКС  для  Заяв  вступників  та  СКБ"
)

ds0 %>% glimpse()
ds_names <- 
  ds0 %>% slice(1) %>% t() %>% 
  as_tibble() %>%
  rename(
    ua_name = V1
  ) 

ds1 <- 
  ds0 %>% 
  slice(2:nrow(ds0)) # Because it contains the names of the columns

names(ds1) <- names(var_names)
ds_names  %>% print(n=nrow(.))
ds0 %>% glimpse()
ds1 %>% glimpse()
```

# Tweek data 2

We can see that the *"index_2024"* directly proportional to *"rank_2024"*

We can see that the *"qs_index"* directly proportional to *"qs_rank"*

Also, the lowest value of *"qs_rank"* is 7

```{r}
#| label: tweek-data-2
#| code-summary: Preparing data to use 
#| warning: false
#| results: false
#| code-fold: true

convert_to_numeric <- function(x) {
  # Replace comma with dot
  x <- gsub(",", ".", x)
  # Convert to numeric
  as.numeric(x)
}

varnames_in_ds1 <- names(ds1)
varnames_to_convert_to_numeric <- setdiff(varnames_in_ds1, "school_name")

ds2 <- 
  ds1 %>% 
  mutate_at(
    .vars = varnames_to_convert_to_numeric
    ,.funs = ~convert_to_numeric(.)
  ) %>%  
  left_join(
    y = ds_school_meta %>% select(rank_2024, student_body_2024)
    ,by = "rank_2024"
  ) %>% 
  mutate(
    student_body_2024 = as.numeric(student_body_2024)
  )

ds3<- ds_school_meta %>%
  left_join(ds_school_meta2, by = "school_name")  %>% 
  slice(1:50)

ds4 <- ds2 %>% 
  slice(1:50) %>% 
  left_join(ds3, by = "rank_2024") %>% 
  select(-school_name.x) %>% 
  select(-student_body_2024.x) %>% 
  rename(
    student_body_2024 = student_body_2024.y
    ,school_name = school_name.y
         ) %>% 
  select(rank_2024,school_name,school_abb, index_2024, student_body_2024,city,oblast,num_requests, mean_bal, num_budget, num_faculty, num_specility, scopus_rank, scopus_index, webometrics_rank, webometrics_index, qs_rank, qs_index, uimpact_rank, uimpact_index, wur_rank, wur_index, qswur_rank, qswur_index, competition_rank, competition_index, patent_rank, patent_index, naqa_rank)
  
ds4 %>% glimpse()
ds3 %>% glimpse()  
ds_school_meta %>% glimpse()
ds2 %>% glimpse()
```

# Exploring

```{r}
#| label: inspect-data-1
#| code-summary: Explore data before tweaking any further

# Let's explore the relationship between ranks and indices

# Overal Rank and Index according to the EuroOsvita method
ds2 %>% glimpse()
ds2 %>% 
  ggplot(aes(x=rank_2024, y = index_2024))+
  geom_point(shape = 21)+
  labs(
    title = "Relationship between index and rank"
  )

# QS
# All universities which has qs rank higher than 7, only  are on QS website. Universities which are not on the website have rank 7.
ds2 %>% 
  ggplot(aes(x=qs_rank, y = qs_index, color = as.factor(qs_rank)))+
  # geom_point(shape = 21)+
  geom_jitter(shape = 21)+
  labs(
    title = "Relationship between index and rank"
  )

# TODO: study the difference between geom_histogram vs geom_col
# be ready to explain the difference and when it makes sense to use each
ds2 %>% 
  group_by(qs_index) %>% 
  summarize(
    count = n()
  ) %>% 
  print() %>% 
  ggplot(aes(x=qs_index, y = count))+
  geom_col()

ds2 %>% 
  ggplot(aes(x=qs_index))+
  geom_histogram() # hint: look up default geom_stat
  
# Scopus
ds2 %>% 
  ggplot(aes(x=scopus_rank, y = scopus_index))+
  # geom_point(shape = 21)+
  geom_jitter(shape = 21)+
  labs(
    title = "Relationship between index and rank"
  )

ds2 %>% select(scopus_rank, scopus_index) %>% summary()  

ds2 %>% 
  group_by(scopus_rank) %>% 
  summarize(
    count = n()
  ) %>% 
  ungroup() %>% 
  filter( count > 1L)
   

ds2 %>% 
  select(1:3, scopus_rank, scopus_index) %>% 
  filter( scopus_rank == 202L)

# Webometricx
ds2 %>% 
  ggplot(aes(x=webometrics_rank, y = webometrics_index))+
  # geom_point(shape = 21)+
  geom_point(shape = 21)+
  labs(
    title = "Relationship between index and rank"
  )

ds2 %>% 
  group_by(webometrics_rank) %>% 
  summarize(
    count = n()
  ) %>% 
  ungroup() %>% 
  filter(count > 1L)


ds2 %>% 
  ggplot(aes(x=webometrics_index))+
  geom_histogram()

# University Impact
ds2 %>% 
  ggplot(aes(x=uimpact_rank, y = uimpact_index))+
  # geom_point(shape = 21)+
  geom_jitter(shape = 21)+
  labs(
    title = "Relationship between index and rank"
  )

ds2 %>% 
  group_by(uimpact_index) %>% 
  summarize(
    count = n()
  ) %>% 
  ungroup()

# The WUR index

# The rate of top local universities according to Times Higher Education ("THE World University Ranking 2024") 

ds2 %>% 
  ggplot(aes(x = wur_rank, y = wur_index)) + 
  #geom_point()
  #geom_jitter()
  geom_col()


ds2 %>% 
  group_by(wur_index) %>% 
  summarize(
    count = n()
  ) %>% 
  ungroup()

ds2 %>% 
  group_by(wur_rank) %>% 
  summarise(
    count = n()
  ) %>% 
  ungroup() #%>% 
  #filter( count > 1)

# QS  WUR  Sustainability

# This rank helps to understand how universitis refer to climatic problems

ds2 %>% 
  ggplot(aes(x= qswur_rank, y = qswur_index))+ 
  #geom_point()
  #geom_jitter()
  geom_col()

ds2 %>% 
  group_by(qswur_rank) %>% 
  summarise(
    count = n()
  ) %>% 
  ungroup()

ds2 %>% 
  group_by(qswur_index) %>% 
  summarise(
    count = n()
  ) %>% 
  ungroup() %>% 
  filter( count > 1L)


# Competion rank


# Dercribes how effective and often the university is involved in differendt scintist projects.

ds2 %>% 
  ggplot(aes(x= competition_rank, y = competition_index)) +
  geom_point()

ds2 %>% 
  group_by(competition_rank) %>% 
  summarise(
    count = n()
  ) %>% 
  ungroup() %>% 
  filter( count > 1) %>% 
  print(n = Inf)
ds2 %>% 
  group_by(competition_index) %>% 
  summarise(
    count = n()
  ) %>% 
  ungroup() %>% 
  #filter( count > 1) %>% 
  print(n = Inf)

# NAQA rate

ds2 %>% 
  ggplot(aes(x = naqa_rank, y = naqa_index))+
  geom_point()

ds2 %>% 
  group_by(naqa_rank) %>% 
  summarise(
    count = n()
  ) %>% 
  ungroup() %>% 
  #filter(count > 1) %>% 
  print(n = Inf)
ds2 %>% 
  group_by(naqa_index) %>% 
  summarise(
    count = n()
  ) %>% 
  ungroup() %>% 
  #filter(count > 1) %>% 
  print(n = Inf)

# Patent Rate

# The higher rank the more patents have university 

ds2 %>% 
  ggplot(aes(x = patent_rank, y = patent_index)) +
  geom_point()

ds2 %>% 
  group_by(patent_rank) %>% 
  summarise(
    count = n()
  ) %>% 
  ungroup() %>% 
  filter(count > 1) %>% 
  print(n = Inf) 
ds2 %>% 
  group_by(patent_index) %>% 
  summarise(
    count = n()
  ) %>% 
  ungroup() %>% 
  filter(count > 1) %>% 
  print(n = Inf) 

ds2 %>% 
  ggplot(aes(x = patent_rank)) + 
  geom_bar()

# Mean rank

ds2 %>% 
  ggplot(aes(x = mean_rank, y = mean_index)) + 
  #geom_point()
  geom_col()
ds2 %>% 
  ggplot(aes(x = mean_rank)) + 
  geom_bar()

ds2 %>% 
  group_by(mean_rank) %>% 
  summarise(
    count = n()
  ) %>% 
  ungroup() %>% 
  print(n = Inf)

# ------- Exploring --------

ds2 %>%
  filter(
competition_index == min(competition_index)
  ) %>% 
  select(competition_rank,competition_index) %>% 
  tibble() %>% 
  print(n = Inf)


ds2 %>% 
  filter(
    naqa_index == min(naqa_index)
  ) %>% 
  select(naqa_rank, naqa_index) %>% 
  tibble()

# From https://euroosvita.net/index.php/?category=1&id=8252, we know that the min index that affect on university is 0.055. So, 0.055 is the lowest possible index.

ds2 %>%
  slice_min(competition_index, n = 3) %>%
  select(competition_rank,competition_index) %>% 
  tibble() %>% 
  print(n = Inf)

ds2 %>% 
  slice_min(naqa_index, n = 3) %>% 
  select(naqa_rank, naqa_index) %>% 
  tibble()
 
# The further values in the table naqa_index and competition_index are multiple to 0.055.

#-----Exploring№2-----
ds2 %>% 
  slice_min(wur_index, n = 2) %>% 
  select(wur_rank, wur_index) %>% 
  tibble()
# From https://euroosvita.net/index.php/?category=1&id=8252, the lowest possible value is 0.150

ds2 %>% 
  slice_min(qs_index, n = 2) %>% 
  select(qs_rank, qs_index) %>% 
  tibble()

ds2 %>% 
  slice_min(scopus_index, n = 2) %>% 
  select(scopus_rank, scopus_index) %>% 
  tibble()

# This is confirmation that higher position in each rank the lower possible index the university have in the table, another university have multiple indexs in the table to lowest. For example: Rank 1 in scopus_rank has index 0.13 in scopus_index, rank 2 in scupus_rank has index 0.26 (that twise 0.13)

# Adding to each rank the priority:
# 1 == Rank 2024
# 2 == Scopus rank
# 3 == Webometric rank
# 4 == QS rank
# 5 == Uimpact rank
# 6 == WUR rank
# 7 == QSwur rank
# 8 == Competition rank
# 9 == Patent rank
# 10 == Naqa rank
#------ Information------

# Tools for exploring distributions of ranks and indices:

## Univariate:
# histogram
# bar plot

## Bivariate:
# scatter plot


```

# Graph 2

```{r}
#| label: graph-2
#| code-fold: true
#| results: hold
#| code-summary: Graph 2
#| warning: false

ds4 %>% 
  ggplot(aes(x = rank_2024, y = student_body_2024)) + 
  geom_point(aes(
    fill = case_when(
      student_body_2024 > 19300 ~ city,           
      rank_2024 <= 23 ~ city,                   
      TRUE ~ "Other"                             
    ), alpha = case_when(
      student_body_2024 > 19300 ~ 1,           
      rank_2024 <= 23 ~ 1,                   
      TRUE ~ 0.5
    )
  ), shape = 21, size = 2.3) +  
  scale_fill_manual(
    values = c("Kyiv" = "gold", "Lviv" = "green", "Other" = "black", "Kharkiv" = "blue", "Sumy" = "lightgreen", "Odesa" = "lightblue", "Dnipro" = "red", "Vinnytsia" = "purple", "Chernivtsi" = "brown" )  
  ) + 
  scale_alpha_identity() +
  theme_minimal() + 
  labs(
    x = "Rank 2024"
    , y = "Number of students"
    , fill = "Сity"
    , alpha = "Top uni"
    , title = "Top 50 universities in Ukrain"
    , subtitle = "Top 50 universities depends on their location"
  )

ds4 %>% 
  group_by(city) %>% 
  summarise(
    count = n()
  ) %>% 
  ungroup() %>% 
  arrange(desc(count))
```

# Graph 1

Graph shows the relation between Scopus rank and Rank 2024.

The red means that the university has higher position in **Scopus rank** than in **Rank 2024**

The blue mean that the university has higher position in **Rank 2024** than in **Scopus rank**

Squares mean that the university has higher rank in QS Rate than 7, the bigger square is the better rank the university has.

The more visible objects are the more students teaching there.

```{r}
#| label: graph-1
#| code-fold: true
#| results: hold
#| code-summary: Graph 1
#| warning: false

ds2_scopus <- 
  ds2 %>% 
  filter(
    rank_2024 <= 50,
    scopus_rank > rank_2024
  )

ds2_scopus_high_qs <- 
  ds2_scopus %>% 
  filter(
    rank_2024 <= 50,
    qs_rank < 7
  )
ds2_scopus_low_qs <- 
  ds2_scopus %>% 
  filter(
    rank_2024 <= 50,
    qs_rank == 7
  )

ds2_rank <- 
  ds2 %>% 
  filter(
    rank_2024 <= 50,
    rank_2024 > scopus_rank
  )

ds2_rank_high_qs <- 
  ds2_rank %>% 
  filter(
    rank_2024 <= 50,
    qs_rank < 7
  )
ds2_rank_low_qs <- 
  ds2_rank %>% 
  filter(
    rank_2024 <= 50,
    qs_rank == 7
  )

g1 <- 
  ds2 %>% 
  filter(
    rank_2024 <= 50
  ) %>% 
  ggplot(aes(x = rank_2024, y = scopus_rank)) + 
  geom_point(data = ds2_scopus_low_qs, aes(size = 1 / qs_rank, alpha = student_body_2024), color = "red", shape = 21, fill = "grey", size = 3) +
  geom_point(data = ds2_scopus_high_qs, aes(size = 1 / qs_rank, alpha = student_body_2024), color = "red", shape = 22, fill = "grey") +
  geom_point(data = ds2_rank_low_qs, aes(size = 1 / qs_rank, alpha = student_body_2024), color = "blue", shape = 21, fill = "grey", size = 3) +
  geom_point(data = ds2_rank_high_qs, aes(size = 1 / qs_rank, alpha = student_body_2024), color = "blue", shape = 22, fill = "grey" ) +
  #geom_point(data = ds2_kyiv_kpi, shape = 21, fill = "gold", color = "black", size = 5, stroke = 1.5) +  
   guides(alpha = guide_legend(override.aes = list(shape = 21, color = "grey",fill = "grey"))) +
   guides(size = guide_legend(override.aes = list(shape = 22, color = "black", fill = "grey"))) +
  #guides(color = guide_legend(title = "Category")) +
  scale_size_continuous(range = c(3, 6)) +  
  scale_alpha_continuous(
    range = c(0.2, 1),
    breaks = c(1000, 2000, 5000, 10000, 20000, 30000, 40000),  
    labels = c("1k", "2k", "5k", "10k", "20k", "30k", "40k")
  ) +
  #scale_color_manual(
    #values = c(
       #"Universities which have higher rank in Scopus rank than in Rank 2024 in Ukraine"= "red",
       #"Universities which have higher rank in Rank 2024 in Ukraine than in Scopus rank" = "blue"
    #)
  #) +
  labs(
    size = "QS Rank",
    alpha = "Number of students",
    x = "Rank 2024 in Ukraine",
    y = "Scopus rank",
    title = "Relation between scopus and 2024 ranks",
    subtitle = "The number of top 50 universities in Ukraine",
    caption = "by Oleksandr Koval"
    ) +         
  theme_minimal()

g1

```

You can see on this graph:

1.  Relation between **Scopus rank** and **Rank 2024 in Ukraine**
2.  Universities which have higher rank in *Scopus rank* than in *Rank 2024 in Ukraine* (on graph have red color)
3.  Universities which have higher rank in *Rank 2024 in Ukraine* than in *Scopus rank* (on graph have blue color)
4.  The universities which have higher rank of **QS rate** than 7 (On graph show as a squares, the higher rate it have the bigger square is)
5.  The number of students who are studying there (On graph the more visible objects are the more students studying there)