---
title: "Difference"
author: "Oleksandr Koval"
format: 
  html: 
    toc: true
    toc-location: right
editor: visual
---

# Difference between geom_bar and geom_col

On this page we will see the difference geom_bar and geom_col

# Creating data

```{r}
#| Label: Preparing
#| warning: false


library(tidyverse)
library(ggplot2)

b <- c(1, 2, 3, 4, 5, 6, 7, 8, 9, 10) %>% tibble()
c <- c(19, 37, 58, 9, 12, 35, 72, 15, 15, 13) %>% tibble()

ds0 <- 
  bind_cols(b, c) %>%  # Use bind_cols instead of cbind
  setNames(c("x", "y"))  # Rename columns

ds0 %>% 
  tibble() %>% 
  glimpse()



```

# Using geom_bar

## Creating and displaying ds_x

```{r}
#| Label: Explanation 1
#| code-summary: How we use geom_bar
#| results: markup

ds_x <- 
  ds0 %>% 
  select(x)

ds_x %>% 
  ggplot(aes(x = x)) + 
  geom_bar()

ds_x %>% 
  group_by(x) %>% 
  summarise(
    count = n()
  ) %>% 
  ungroup() %>% 
  print(n = Inf)# We can see that in every row in "x" we have only 1 value
```

We can see that in every row in "x" we have only 1 value

## Creating and displaying ds_y

```{r}
ds_y <- 
  ds0 %>% 
  select(y)

ds_y %>% 
  ggplot(aes(x = y)) + 
  geom_bar()

ds_y %>% 
  group_by(y) %>% 
  summarise(
    count = n()
  ) %>% 
  ungroup() 



```

```{r}
#| Label: Explanation 
#| code-summary: Explanation
ds_y %>% 
  group_by(y) %>% 
  summarise(
    count = n()
  ) %>% 
  ungroup() %>% 
  filter(count > 1) # We can see that the bar higher where the count of values is 2
```

We can see that the bar higher where the count of values is 2

**So, if we use geom_bar we can see the relation between column or object and the number of values in this object. In geom_bar using only one argument.**

# Using geom_col

In geom_col we need to use two arguments, because the function is the same as geom_point.

```{r}
#| Label: Explanation 2
#| warning: false
g1 <- 
ds0 %>% 
  ggplot(aes(x = x, y = y))+
  geom_col() # We can see that graph display relation between two arguments: x and y. 

g2 <- 
ds0 %>% 
  ggplot(aes(x = x, y = y)) +
  geom_point() # We can see that graph display relation between two arguments: x and y

g1 
g2 
```

We use geom_col to describe the relation between two arguments on the graph. Only thing that is different in g1 and g2 is the way of displaying an information
